Supplementary Information: Improving Monocular Depth Estimation with Global Depth Histogram Matching

### 2019-10-17 paper/cvpr2020/sections/supplement/hardware_comparison.tex
Updated method figure and supplement.
Working on supplement, revised get_hist_med to actually get the median.

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\

@@

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

@@

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}

%% MiDaS outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_29_kitchen_scene/rmses.tex}& \\

@@

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

@@

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured}
%    \vspace{-1.5em}
\end{figure*}
%% DenseDepth outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_29_kitchen_scene/rmses.tex}& \\

@@

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densdepth_captured}
%    \vspace{-1.5em}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

>>>>

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\

@@

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground
      truth. MiDaS does not output metric depth, so the CNN depth maps are
      scaled to be in the range $(0.494, 9.094)$ by default. However, MiDaS does produce
      accurate ordinal depth, leading to stronger performance of our histogram
      matching compared to other methods.}
    \label{fig:midas_captured_1}
%    \vspace{-1.5em}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

@@

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.MiDaS does not output metric depth, so the CNN depth maps are
      scaled to be in the range $(0.494, 9.094)$ by default. However, MiDaS does produce
      accurate ordinal depth, leading to stronger performance of our histogram
      matching compared to other methods.}
    \label{fig:midas_captured_2}
%    \vspace{-1.5em}
\end{figure}

% %% MiDaS outdoor scene
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground
      truth. MiDaS does not output metric depth, so the CNN depth map is
      scaled to be in the range $(0.494, 11.094)$ by default. However, MiDaS does produce
      accurate ordinal depth, leading to stronger performance of our histogram
      matching compared to other methods.
}
    \label{fig:midas_captured_3}
%    \vspace{-1.5em}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_29_kitchen_scene/rmses.tex}& \\

@@

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured_1}
%    \vspace{-1.5em}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

@@

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured_2}
%    \vspace{-1.5em}
\end{figure}
%% DenseDepth outdoor scene
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured_3}
%    \vspace{-1.5em}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_29_kitchen_scene/rmses.tex}& \\

@@

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_captured_1}
%    \vspace{-1.5em}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\
